---
title: "A review on the first few lectures"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Quick review of April 13th session

Using R as a calculator:

```{r}
2*8+3
2^3*5-3
a <- 2^3*5-3
a-6
```

Using print and paste:

```{r}
print("It's a good day!")
print(paste("I am", a, "years old."))
print(paste("I am", a, "years old.", sep="-"))
```

Getting help from R:

```{r, eval=FALSE}
help(read.table)
?read.table
```

Creating vectors:

```{r}
weight.1 <- c(112,106,121,119)
weight.2 <- c(122,136,133,140)
weight.2-weight.1
```

Testing, and log variables:

```{r}
fruits <- c("Apple","Orange","Carrot")
fruits=="Apple"
isApple <- fruits=="Apple"
isApple
```

Factors are categorical variables. Those are necessary to distinguish between categorical and numerical variables:

```{r}
pain <- c(0,3,2,2,1)
pain
levels(pain)
levels(as.factor(pain))
levels(pain) <- c("none","mild","medium","severe")
levels(pain)
pain
```

## Quick review of April 14th session

Sequences:

```{r}
4:9
seq(4,9)
seq(4,9,1)
seq(4,10,2)
```

Replicates:

```{r}
oops <- c(7,9,13)
rep(oops,3)
rep(oops,1:3)
rep(c("male","female"),c(4,6))
rep(c("male","female"),each=5)
```

Lists are useful to combine different collection of objects.

```{r}
intake.pre <- c(5260,5470,5640,6180,6390,6515,6805,7515,7515,8230,8770)
intake.post <- c(3910,4220,3885,5160,5645,4680,5265,5975,6790,6900,7335)
mylist <- list(before=intake.pre, after=intake.post)
mylist
mylist$after
```

Matrices:

```{r}
x <- 1:12
dim(x) <- c(3,4)
x
y <- matrix(1:12,nrow=3,byrow=TRUE)
y
dim(x)
```

Data frame is the most useful way to deal with a table-like data. Creating a data frame:

```{r}
testdata <- data.frame(id=paste('pig',1:9,sep=""),pre.weaning=101:109,post.weaning=209:201)
testdata
testdata$id
testdata$post.weaning
testdata$post.weaning[2]
```

Slicing:

```{r}
test <- data.frame(x=1:5,y=6:10,z=11:15)
test
test[,2]
test[2,]
test[2,2]
test[2,c(1,3)]
```

Indexing:

```{r}
colnames(test) <- c("xx","yy","zz")
rownames(test) <- c("a","b","c","d","e")
test
test[,"yy"]
test["b",]
test["b","yy"]
test["b",c("xx","zz")]
subset(test, select=xx)
subset(test, select=-xx)
```

Slicing & indexing:

```{r}
test[1:3,c("xx","zz")]
```

Dropping data:

```{r}
test
test[,-1]
test[-1,]
subset(test,select=-xx)
```

Conditional selection:

```{r}
test
test[test$xx!=3,]
test[test$xx>3,]
test[test$xx>=3 & test$zz<=14,]
test[test$xx>3 | test$zz<12,]
```

Read data file:

To read a space separated file like [`data1.txt`](https://drive.google.com/uc?export=download&id=0B2l_izQwJmVpQ2tnbVp5cU90SDA), with a header row:
Depending to the file that you are reading, options can be different.

```{r, eval=FALSE}
data1 <- read.table(file.choose(), header=TRUE, colClasses=c("character","character","numeric","numeric"))
```

```{r, echo=FALSE}
data1 <- read.table("data1.txt", header=TRUE, colClasses=c("character","character","numeric","numeric"))
```

Get some information about the file:

```{r}
colnames(data1)
head(data1)
head(data1,10)
tail(data1)
dim(data1)
ncol(data1)
nrow(data1)
summary(data1)
```

## Quick review of April 15th session

For the solutions of the home work, check the presentation file.

Write data file:

> Let say we want to write the first 100 rows of `data1` in a space separated file `data1small.txt`, with header row, no quotes, and no row names:
> Depending to the file that you want to write, options can be different.

```{r, eval=FALSE}
write.table(data1[1:100,], file="data1small.txt", quote=FALSE, row.names=FALSE)
getwd()
```

You can write notes and outputs to an external file. Consider the following example:

```{r, eval=FALSE}
write(file="log.txt", print("This is my log file."))
write(file="log.txt", print(paste("Birth weight average =", mean(data1$birthw))), append=TRUE)
write(file="log.txt", print(paste("Weaning weight average =", mean(data1$weanw))), append=TRUE)
```

In `log.txt`, you would have:

```
This is my log file.
Birth weight average = 4.9986
Weaning weight average = 17.1162"
```

To view a data in RStudio, either click the data in the Environment window or:

```{r, eval=FALSE}
View(data1)
```

To start editing the data manually:

```{r, eval=FALSE}
edit(data1)
```

You can get many descriptive statistics from your data. For example:

```{r}
mean(data1$birthw)
cor(data1$birthw, data1$weanw)
```

Merging 2 data frames (different options are used. Checkout the differences):

```{r}
df1 <- data.frame(anim=paste0('anim',1:9), food=19:11)
df2 <- data.frame(anim=paste0('anim',2:10),water=22:30)
df1
df2
df3 <- merge(df1, df2, by="anim")
df3
df3 <- merge(df1, df2, by="anim", all.x=TRUE)
df3
df3 <- merge(df1, df2, by="anim", all.y=TRUE)
df3
```

What if the by column has different names in the 2 data sets?!

```{r}
colnames(df2)[1] <- "animal"
colnames(df1)
colnames(df2)
df3 <- merge(df1, df2, by.x="anim", by.y="animal")
df3
```

cbind

To do `cbind`, the data frames should have the same number of rows.

```{r}
df1
df2
df3 <- cbind(df1, df2)
df3
```

rbind

To do `rbind`, the data frames should have the same number of columns and the same column names.

```{r}
colnames(df1) <- c("anim","food_water")
colnames(df2) <- c("anim","food_water")
df3 <- rbind(df1, df2)
df3
```

sort

`sort` is not made for data frames! It is for vectors or a single column in a data frame.

```{r}
df1 <- data.frame(anim=paste0('anim',1:9), food=19:11)
df2 <- data.frame(anim=paste0('anim',2:10),water=22:30)
df3 <- merge(df1, df2, all.x=TRUE)
df3
sort(df3$food)
sort(df3$food, decreasing=TRUE)
```

order

Example of the `order` command:

```{r}
df3[order(df3$food),]
df3[order(-df3$food),]
df3$group <- rep(1:3,3)
df3
df3[order(-df3$group, df3$food),]
```

Matrix operations (not presented, but slides are available for those who are interested.)
