\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{url}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{\LARGE Mohammad Ali Nilforooshan} \hfill {\em Quantitative Geneticist}

\begin{resume}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Contact Information}

\vspace{.05in}
\begin{tabular}{@{}p{3.5in}p{3in}}
LIC                        & {E-mail:}  mohammad.nilforooshan@lic.co.nz \\
Private Bag 3016           & {Website:} \url{https://nilforooshan.github.io} \\
Hamilton 3240, New Zealand & {GitHub:}  \url{https://github.com/nilforooshan} \\
 & {Google Scholar:} \url{https://goo.gl/iKbCoU}
\end{tabular}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Interests}

Matrix Algebra \\
Statistical methods applied to livestock genetic and genomic evaluation \\
Putting biology into equations and equations into program codes \\
Single-step genomic evaluation \\
Computational biology \\
Traveling
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Education}

{\bf Swedish University of Agricultural Sciences, Dept. Animal Breeding and Genetics} \\
PhD in Animal Breeding and Genetics -- Quantitative Genetics, June 2007 -- May 2011
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Awards}

\begin{list2}
\item Grant from Interbull Centre for participation in the 9th World Congress on Genetics Applied to Livestock Production (2010), Leipzig, Germany
\item Grant from FUR foundation (SLU funds for internationalization of postgraduate studies) for participation in the 60th Annual meeting of the European Association for Animal Production (2009), Barcelona, Spain
\item Scholarship from the Guest Scholarship Program (2008) of the \href{https://si.se/en}{Swedish Institute}
\item Grant from FUR foundation (SLU funds for internationalization of postgraduate studies) for participation in the 59th Annual meeting of the European Association for Animal Production (2008), Vilnius, Lithuania
\end{list2}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Skills}

{\bf Scientific:} Matrix Algebra, Quantitative Genetics and General Animal Breeding, Statistics, "Big Data", Reviewer for scientific journals \\
{\bf Programming:} R, SAS, Fortran, Linux Shell scripting (Sed and Awk), Python, Markdown and RMarkdown, Git and GitHub, Docker, Julia (beginner), and C (beginner) \\
{\bf Analytics:} Designing, streamlining and documenting genetic/genomic evaluation pipelines; experienced in several computer packages such as ASReml, DFReml, MiX99 and BLUPF90
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Professional Experience}

{\bf LIC} \\
{\em Scientist -- Quantitative Genetics} \hfill{May 2020 -- Present}

{\bf LIC} \\
{\em Postdoctoral Research Fellow in Quantitative Genetics} \hfill{December 2018 -- May 2020}

{\bf University of Otago}, Dept. Mathematics and Statistics \\
{\em Postdoctoral Fellow in Quantitative Genetics} \hfill{November 2015 -- October 2018}

{\bf Swedish University of Agricultural Sciences}, \\
Dept. Animal Breeding and Genetics, Interbull Centre \\
{\em Geneticist} \hfill{June 2012 -- October 2015}

{\bf University of Nebraska-Lincoln}, Dept. Statistics \\
{\em Postdoctoral Research Fellow in Computational Biology} \hfill{September 2011 -- May 2012}

{\bf Isfahan Science and Technology Town}, Animal Science Core \\
{\em Research Assistant} \hfill{September 2004 -- June 2006}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Teaching}

\begin{list2}
\item Supervising a visiting PhD student to the Department of Mathematics and Statistics, University of Otago, August -- October, 2018.
\item Teaching some lectures of the postgraduate course in Quantitative Genetics, held at the University of Otago, Dunedin, New Zealand, July -- October, 2018.
\item Teaching some lectures of the postgraduate course in Quantitative Genetics, held at the University of Otago, Dunedin, New Zealand, July -- October, 2017.
\item Teaching R programming, and giving several other talks in the University of Chapingo, Texcoco, Mexico, April 2015.
\item Teaching "Dairy Cattle Husbandry" in Kabootar-Abad school of Agriculture, Isfahan, Iran, September 2004 -- June 2005.
\end{list2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Software}

{\bf Nilforooshan, M.A.} 2020. R package \href{https://CRAN.R-project.org/package=pedSimulate}{pedSimulate}: Pedigree, Genetic Merit and Phenotype Simulation. \\
{\bf Nilforooshan, M.A.} 2019. R package \href{https://CRAN.R-project.org/package=mbend}{mbend}: Matrix Bending. \\
{\bf Nilforooshan, M.A.} 2019. R package \href{https://CRAN.R-project.org/package=ggroups}{ggroups}: Pedigree and Genetic Groups.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Editorial Contributions}

Frontiers in Genetics -- Section Livestock Genomics: \href{https://www.frontiersin.org/research-topics/24065/reducing-the-environmental-footprint-of-livestock-through-genomic-selection}{Reducing the Environmental Footprint of Livestock Through Genomic Selection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Publications}

\begin{list2}

\item Saavedra-Jim\'{e}nez, L.A., R. Ram\'{i}rez-Valverde, R. N\'{u}\~{n}ez-Dom\'{i}nguez, A. Ru\'{i}z-Flores, J.G. Garc\'{i}a-Mu\~{n}iz, and {\bf M.A. Nilforooshan}. 2021. Effect of two phantom parent grouping strategies on the genetic evaluation of growth traits in Mexican Braunvieh cattle. {\em Rev. Mex. Cienc. Pecu.} Accepted.
\item {\bf Nilforooshan, M.A.}, D. Garrick, and B. Harris. 2021. Alternative ways of computing the numerator relationship matrix. {\em Front. Genet.} 12:1236. \href{https://www.frontiersin.org/articles/10.3389/fgene.2021.655638}{doi:10.3389/fgene.2021.655638}
\item {\bf Nilforooshan, M.A.}, and D. Garrick. 2021. Reduced animal models fitting only equations for phenotyped animals. {\em Front. Genet.} 12:372. \href{https://www.frontiersin.org/article/10.3389/fgene.2021.637626}{doi:10.3389/fgene.2021.637626}
\item {\bf Nilforooshan, M.A.} 2020. mbend: An R package for bending non-positive-deﬁnite symmetric matrices to positive-deﬁnite. {\em BMC Genet.} 21: 97. \href{https://doi.org/10.1186/s12863-020-00881-z}{doi:10.1186/s12863-020-00881-z}
\item {\bf Nilforooshan, M.A.}, and L.A. Saavedra-Jim\'{e}nez. 2020. ggroups: An R package for pedigree and genetic groups data. {\em Hereditas} 157: 17. \href{https://doi.org/10.1186/s41065-020-00124-2}{doi:10.1186/s41065-020-00124-2}
\item {\bf Nilforooshan, M.A.} 2020. Memory-efficient self-cross-product for large matrices using R and Python. {\em J. Math. Comput. Sci.} 10(3): 497--506. \href{https://doi.org/10.28919/jmcs/4457}{doi:10.28919/jmcs/4457}
\item {\bf Nilforooshan, M.A.} 2020. Updating genetic relationship matrices and their inverses: A methodology note. {\em Can. J. Anim. Sci.} 100(2): 292--298. \href{https://doi.org/10.1139/CJAS-2019-0106}{doi:10.1139/CJAS-2019-0106}
\item {\bf Nilforooshan, M.A.} 2020. Application of single-step GBLUP in New Zealand Romney sheep. {\em Anim. Prod. Sci.} 60(9): 1136--1144. \href{https://doi.org/10.1071/AN19315}{doi:10.1071/AN19315}
\item {\bf Nilforooshan, M.A.}, and M. Lee. 2019. The quality of the algorithm for proven and young with various sets of core animals in a multibreed sheep population. {\em J. Anim. Sci.} 97(3): 1090--1100. \href{https://doi.org/10.1093/jas/skz010}{doi:10.1093/jas/skz010}
\item {\bf Nilforooshan, M.A.}, J.H. Jakobsen, W.F. Fikse, B. Berglund, and H. Jorjani. 2014. Multiple-trait multiple country genetic evaluation of Holstein bulls for female fertility and milk production traits. {\em animal} 8(6) 887--894. \href{https://doi.org/10.1017/S1751731114000895}{doi:10.1017/S1751731114000895}
\item Behdad, S., M.A. Edriss, {\bf M.A. Nilforooshan}, and A.H. Movassagh. 2013. Wool characteristics of Bakhtiari sheep and the correlated responses to selection for pre-weaning daily gain. {\em Indian J. Anim. Sci.} \href{http://epubs.icar.org.in/ejournal/index.php/IJAnS/article/view/26453}{83(1): 82--85}.
\item {\bf Nilforooshan, M.A.} 2011. Multiple-trait multiple country genetic evaluation of fertility traits in dairy cattle. Uppsala : Sveriges lantbruksuniv., {\em Acta Universitatis Agriculturae Sueciae}, 1652-6880 ; 2011:31. ISBN 978-91-576-7566-8. \href{https://pub.epsilon.slu.se/8094}{Doctoral thesis}.
\item {\bf Nilforooshan, M.A.}, W.F. Fikse, B. Berglund, J.H. Jakobsen, and H. Jorjani. 2011. Short communication: Quantifying bias in a single-trait international model ignoring covariances from multiple-trait national models. {\em J. Dairy Sci.} 94: 2631--2636. \href{https://doi.org/10.3168/jds.2010-3863}{doi:10.3168/jds.2010-3863}
\item {\bf Nilforooshan, M.A.}, J.H. Jakobsen, W.F. Fikse, B. Berglund, and H. Jorjani. 2010. Application of a multiple-trait multiple-country genetic evaluation model for female fertility traits. {\em J. Dairy Sci.} 93: 5977--5986. \href{https://doi.org/10.3168/jds.2010-3437}{doi:10.3168/jds.2010-3437}
\item {\bf Nilforooshan, M.A.} 2010. Contemporary grouping in mixed size dairy herds experiencing four seasons. {\em Turk. J. Vet. Anim. Sci.} 34: 129--135. \href{https://doi.org/10.3906/vet-0710-18}{doi:10.3906/vet-0710-18}
\item {\bf Nilforooshan, M.A.}, A. Khazaeli, and M.A. Edriss. 2008. Effects of missing pedigree information on dairy cattle genetic evaluations. {\em Arch. Tierz., Dummerstorf} 51: 99--110. \href{https://doi.org/10.5194/aab-51-99-2008}{doi:10.5194/aab-51-99-2008}
\item Edriss, M.A., P. Hosseinia, M. Edrisi, H.R. Rahmani, and {\bf M.A. Nilforooshan}. 2008. Prediction of second parity milk performance of dairy cows from first parity information using artificial neural network and multiple linear regression methods. {\em Asian J. Anim. Vet. Adv.} 3(4): 222--229. \href{https://doi.org/10.3923/ajava.2008.222.229}{doi:10.3923/ajava.2008.222.229}
\item Hosseinia, P., M. Edrisi, M.A. Edriss, and {\bf M.A. Nilforooshan}. 2007. Prediction of second parity milk yield and fat percentage of dairy cows based on first parity information using neural network system. {\em J. Applied Sci.} 7(21): 3274--3279. \href{https://doi.org/10.3923/jas.2007.3274.3279}{doi:10.3923/jas.2007.3274.3279}
\item Edriss, M.A., G. Dashab, A.A. Ghare Aghaji, {\bf M.A. Nilforooshan}, and H. Movasagh. 2007. A study on some physical attributes of Naeini sheep wool for textile industry. {\em Pak. J. Biol. Sci.} 10(3): 415--420. \href{https://doi.org/10.3923/pjbs.2007.415.420}{doi:10.3923/pjbs.2007.415.420}
\item {\bf Nilforooshan, M.A.}, and M.A. Edriss. 2007. Comparison of Holstein bull semen sources on milk traits in Isfahan province in Iran. {\em Arch. Tierz., Dummerstorf} 50: 71--83. \href{https://doi.org/10.5194/aab-50-71-2007}{doi:10.5194/aab-50-71-2007}
\item Edriss, M.A., {\bf M.A. Nilforooshan}, and J.M. Sadeghi. 2006. Estimation of direct genetic and maternal effects for production traits of Iranian Holstein cows using different animal models. {\em Pak. J. Biol. Sci.} 9(4): 636--640. \href{https://doi.org/10.3923/pjbs.2006.636.640}{doi:10.3923/pjbs.2006.636.640}
\item Dashab, G., M.A. Edriss, A.A. Ghare Aghaji, H. Movasagh, and {\bf M.A. Nilforooshan}. 2006. Wool fiber quality of Naeini sheep. {\em Pak. J. Biol. Sci.} 9(2): 270--276. \href{https://doi.org/10.3923/pjbs.2006.270.276}{doi:10.3923/pjbs.2006.270.276}
\item {\bf Nilforooshan, M.A.}, and M.A. Edriss. 2004. Effect of age at first calving on some productive and longevity traits in Iranian Holsteins of the Isfahan province. {\em J. Dairy Sci.} 87: 2130--2135. \href{https://doi.org/10.3168/jds.S0022-0302(04)70032-6}{doi:10.3168/jds.S0022-0302(04)70032-6}
\item {\bf Nilforooshan, M.A.} 2003. Genetic Evaluation and Comparison between Domestic and Imported (Canada, USA, Europe) Sperms for Milk Yield, Fat Yield, and Fat Percentage in Some Dairy Farms of Isfahan Province. MSc thesis. \href{https://doi.org/10.5281/zenodo.4297235}{doi:10.5281/zenodo.4297235}
\end{list2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Data and Code}

\begin{list2}
\item {\bf Nilforooshan, M.A.}, D. Garrick, and B. Harris. 2021. Code \& Data -- Alternative Ways of Computing the Numerator Relationship Matrix. {\em figshare}, Journal contribution. \href{https://doi.org/10.6084/m9.figshare.13497939.v1}{doi:10.6084/m9.figshare.13497939.v1}
\item {\bf Nilforooshan, M.A.}, and D. Garrick. 2021. R examples -- Reduced Animal Models Fitting Only Equations for Phenotyped Animals. {\em figshare}, Journal contribution. \href{https://doi.org/10.6084/m9.figshare.13369607.v1}{doi:10.6084/m9.figshare.13369607.v1}
\item {\bf Nilforooshan, M.A.} 2021. mbend: Data, Code \& Results. {\em Mendeley Data}. \href{https://doi.org/10.17632/kf3d8v8939.2}{doi:10.17632/kf3d8v8939.2}
\item {\bf Nilforooshan, M.A.} 2021. Benchmarking matrix self-cross-products, using R and Python functions. {\em Mendeley Data}. \href{https://doi.org/10.17632/vk8vy7ghnf.2}{doi:10.17632/vk8vy7ghnf.2}
\end{list2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Proceedings}

\begin{list2}
\item {\bf Nilforooshan, M.A.}, B. Auvray, and M. Lee. 2018. \href{http://www.wcgalp.org/proceedings/2018/animal-specific-combining-grm-and-nrm-single-step-gblup}{Animal-specific combining of the GRM and the NRM in single-step GBLUP}. {\em 11th World Congress on Genetics Applied to Livestock Production}, Auckland, New Zealand. February, 11--16, 2018. \href{https://drive.google.com/file/d/1cCNViHs-Dyrmbx3PWbbtQv090rVyx0cL/view?usp=sharing}{[poster file}, \href{https://drive.google.com/file/d/1L-yElfdNZz6nx3tB_TwudN3h9PpF5Pxs/view?usp=sharing}{paper]}
\item Pabiou, T., {\bf M.A. Nilforooshan}, E. Venot, and  K. Moore. 2015. \href{https://www.cattlebreeders.org.uk/workspace/documents/2015digest.pdf}{Interbeef presents new opportunities for beef farmers}. {\em British Cattle Conference}, Telford, England. January 19--21, 2015.
\item Pabiou, T., {\bf M.A. Nilforooshan}, D. Laloe, E. Hjerpe, and E. Venot. 2014. \href{http://www.wcgalp.org/proceedings/2014/across-country-genetic-parameters-beef-cattle-interbeef-weaning-weight-genetic}{Across-Country Genetic Parameters in Beef Cattle for Interbeef Weaning Weight Genetic Evaluation}. {\em 10th World Congress on Genetics Applied to Livestock Production}, Vancouver, Canada. August, 17--22, 2014. \href{https://drive.google.com/file/d/0B2l_izQwJmVpVzRvOVl1YnNuWjA/view?usp=sharing}{[poster file]}
\item Venot, E., T. Pabiou, E. Hjerpe, {\bf M.A. Nilforooshan}, A. Launay, and B. Wickham. 2014. \href{http://www.wcgalp.org/proceedings/2014/benefits-interbeef-international-genetic-evaluations-weaning-weight}{Benefits of Interbeef International Genetic Evaluations for Weaning Weight}. {\em 10th World Congress on Genetics Applied to Livestock Production}, Vancouver, Canada. August, 17--22, 2014.
\item M\"{a}ntysaari, E., and {\bf M.A. Nilforooshan}. 2014. \href{https://www.interbull.org/web/static/presentations/Berlin/Wednesday/10_14_Mantysaari.pdf}{Effect of the size of the reference population on the validation reliability of national genomic evaluations}. {\em Interbull Meeting}, Berlin, Germany. May 20--21, 2014.
\item {\bf Nilforooshan, M.A.} 2014. \href{https://journal.interbull.org/index.php/ib/article/view/1360}{A review of the validation of national genomic evaluations}. {\em Interbull Bulletin}. 48: 111--117. {\em Interbull Meeting}, Berlin, Germany. May 20--21, 2014. \href{https://www.interbull.org/web/static/presentations/Berlin/Wednesday/10_01_Nilforooshan.pdf}{[slides file]}
\item {\bf Nilforooshan, M.A.}, and E. Hjerpe. 2014. Interbeef report on weaning genetic evaluation, performed in March 2014 for Charolais and Limousin. {\em Interbeef Technical Meeting}, Uppsala, Sweden. March 10, 2014.
\item Braillon, L., and {\bf M.A. Nilforooshan}. 2013. \href{https://drive.google.com/file/d/0B2l_izQwJmVpYWE2VndwNGhJblU/view?usp=sharing}{Review of the Interbeef proof publication proposal}. {\em Interbeef Technical Meeting}, Nantes, France. August 27, 2013.
\item {\bf Nilforooshan, M.A.}, E. Hjerpe, V. Palucci, and J. D\"{u}rr. 2013. \href{https://drive.google.com/file/d/0B2l_izQwJmVpZ2RRcXc0bS11RmM/view?usp=sharing}{Interbeef report on weaning genetic evaluation for Charolais and Limousin}. {\em Interbeef Technical Meeting}, Aarhus, Denmark. March 27--28, 2013.
\item {\bf Nilforooshan, M.A.} 2012. \href{https://drive.google.com/file/d/0B2l_izQwJmVpLVY5NU1UZGR6czA/view?usp=sharing}{Report on the weaning weight phenotypic data editing for Charolais and Limousin}. {\em Interbeef Technical Meeting}, Uppsala, Sweden. December 6--7, 2012.
\item Jorjani, H., J. Jakobsen, {\bf M.A. Nilforooshan}, E. Hjerpe, B. Zumbach, V. Palucci, and J. D\"{u}rr. 2011. \href{https://journal.interbull.org/index.php/ib/article/view/1250}{Genomic Evaluation of BSW Populations. InterGenomics: Results and Deliverables}. {\em Interbull Bulletin}. 43: 5--8. {\em Interbull Technical Workshop}, Guelph, Ontario, Canada. February 27--28, 2011. \href{https://drive.google.com/file/d/0B2l_izQwJmVpbGh3ZC1iRWhCWVE/view?usp=sharing}{[slides file]}
\item {\bf Nilforooshan, M.A.}, L. R\"{o}nneg\r{a}rd, and H. Jorjani. 2010. \href{http://www.wcgalp.org/proceedings/2010/various-statistical-models-prediction-snp-effects-multi-nationalbreed-reference}{Various statistical models for prediction of SNP effects from a multi-national/breed reference population}. {\em 9th World Congress on Genetics Applied to Livestock Production}, Leipzig, Germany. August 1--6, 2010. \href{https://drive.google.com/file/d/0B2l_izQwJmVpMmxGRzJjMURoTlE/view?usp=sharing}{[poster file]}
\item {\bf Nilforooshan, M.A.}, B. Zumbach, J. Jakobsen, A. Loberg, H. Jorjani, and J. D\"{u}rr. 2010. \href{https://journal.interbull.org/index.php/ib/article/view/1158}{Validation of national genomic evaluations}. {\em Interbull Bulletin}. 42: 56--61. {\em Interbull Meeting}, Riga, Latvia. May 31 to June 4, 2010. \href{https://drive.google.com/file/d/0B2l_izQwJmVpRnlPa0YzS3ZCU1E/view?usp=sharing}{[slides file]}
\item {\bf Nilforooshan, M.A.} 2009. \href{https://drive.google.com/file/d/0B2l_izQwJmVpYW04amtSMGdjUmM/view?usp=sharing}{Developing the method of estimating genetic similarity between populations}. {\em 60th Annual meeting of the European Association for Animal Production}, Barcelona, Spain, Book of Abstracts No. 15: 610. \href{http://old.eaap.org/Previous_Annual_Meetings/2009Barcelona/Papers/53_Nilforooshan.pdf}{[slides file]}
\item {\bf Nilforooshan, M.A.}, J. Jakobsen, F. Fikse, B. Berglund, and H. Jorjani. 2009. \href{https://journal.interbull.org/index.php/ib/article/view/1087}{MT–MACE for female fertility and milk yield}. {\em Interbull Bulletin}. 40: 68--71. {\em Interbull Meeting}, Barcelona, Spain. August 21--24, 2009. \href{https://drive.google.com/file/d/0B2l_izQwJmVpRTlrOGE3OWluVnc/view?usp=sharing}{[slides file]}
\item {\bf Nilforooshan, M.A.} 2009. \href{https://drive.google.com/file/d/0B2l_izQwJmVpUC1TVkx2MVc1ZUE/view?usp=sharing}{International genetic evaluations of fertility traits using MT–MACE}. Faculty research day, Faculty of Veterinary Medicine and Animal Science, Swedish University of Agricultural Sciences, Uppsala, Sweden. December 7, 2009.
\item {\bf Nilforooshan, M.A.} 2009. International genetic evaluations of fertility traits using MT–MACE. 80th Anniversary of the Department of Animal Breeding and Genetics, Swedish University of Agricultural Sciences, Uppsala, Sweden, June 4, 2009.
\item {\bf Nilforooshan, M.A.}, J. Jakobsen, F.W. Fikse, B. Berglund, and H. Jorjani. 2009. \href{https://journal.interbull.org/index.php/ib/article/view/1073}{International genetic evaluations for female fertility traits using multi-trait MACE}. {\em Interbull Bulletin}. 39:99--102. Interbull Workshop on Genomic Information in Genetic Evaluations, Uppsala, Sweden. January 26--29, 2009. \href{https://drive.google.com/file/d/0B2l_izQwJmVpZG1sZlg2cF9zRWc/view?usp=sharing}{[slides file]}
\item {\bf Nilforooshan, M.A.}, F.W. Fikse, and H. Jorjani. 2008. \href{https://drive.google.com/file/d/0B2l_izQwJmVpQWdZaTFwTUNXOFk/view?usp=sharing}{International genetic evaluations of fertility traits considering more than one trait per country}. {\em 59th Annual meeting of the European Association for Animal Production}, Vilnius, Lithuania, Book of Abstracts No. 14: 268. \href{http://old.eaap.org/Previous_Annual_Meetings/2008Vilnius/Papers/published/35_Nilforooshan.pdf}{[slides file]}
\end{list2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\sc Extension}

\href{https://nilforooshan.github.io/resume/extension}{Papers in Farsi}

\end{resume}
\end{document}
% http://quicklatex.blogspot.com/2011/12/latex-video-tutorial-how-to-create.html
% pdflatex resume.tex
